Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-04-24 ms.tex
acknowledge NASA grant

This material is based upon work supported by the National Science Foundation 
Graduate Research Fellowship under Grant No.Based on observations obtained with
 Planck (http://www.esa.int/Planck), an ESA science mission with instruments 
and contributions directly funded by ESA Member States, NASA, and Canada. This 
research made use of the NASA Astrophysics Data System (ADS) and the IDL 
Astronomy User's Library at Goddard. \footnote{Available at 
\texttt{http://idlastro.gsfc.nasa.gov}}

>>>>

This material is based upon work supported by the National Science Foundation 
Graduate Research Fellowship under Grant No. We acknowledge support of NASA 
grant NNX12AE08G for this research. Based on observations obtained with Planck 
(http://www.esa.int/Planck), an ESA science mission with instruments and 
contributions directly funded by ESA Member States, NASA, and Canada. This 
research made use of the NASA Astrophysics Data System (ADS) and the IDL 
Astronomy User's Library at Goddard. \footnote{Available at 
\texttt{http://idlastro.gsfc.nasa.gov}}
